Demo arXiv template

### 2022-11-28 paper/paper.qmd
small tweak on simplification and mark TODOs

**Spatial aggregation**

@@

**Variable transformation **

Variable transformation and scaling, in the next section, are both variable pre-processing steps to prepare the data with desire statistical property to work with. This can be a more stablised variance, a normal distribution that satisfies modelling assumptions, or a data range that required by the algorithms.
Variable tranformation is a general notion of a functional transformation on the variable: $$h_{\tau}(x(\mathbf{s};\mathbf{t})),$$ where $\tau \in T \subseteq \mathbb{R}^{d_{\tau}}$ is the parameter in the transformation, if any, and $d_{\tau}$ is the number of parameter of $\tau$. Typical examples of variable transformation are log, quadratic, square root, and box-cox transformation.

**Scaling**

While scaling can be seen as a specific type of variable tranformation, it is separated into own step to make the scaling operation explicit in the pipeline.
The key difference between the two steps is that variable transformation typically changes the shape of the data while scaling only changes the data scale and can usually be written in the form of $$[x(s_i;t_j) - \alpha]/\gamma.$$
For example, a z-score standardisation can be written in the above form with $\alpha = \bar{x}(s; t)$ and $\gamma = \sigma(s; t)$, a min-max standardisation uses $\alpha = \min[x(s_i, t_j)]$ and $\gamma = \max[x(s_i, t_j)] - \min[x(s_i, t_j)]$.
@fig-scale-var-trans-compare shows a collection of variable pre-processing operations and uses color to differentiate whether the operation is a variable transformation or a scaling step. All the scaling operations in green results in the same shape as the original data.

@@

**Dimension reduction**

@@

**Benchmarking**

@@

In public communication, indexes are often delivered in categorical grades, along with its underlying numerical values. The simplification step, sometimes can also be called discretisation, prescribes how the continuous index values are converted into the discrete grades. This process can be written with the piece-wise function:

@@

where $C_0, C_1,\cdots ,C_z$ are the categories and $c_0, c_1, \cdots, c_z$ are the threshold value in each category. In SPI, drought are sorted into four categories: mild drought: $[-0.99, 0]$; moderate drought: $[-1.49, -1]$; severe drought: $[-1.99, -1.5]$, and extreme drought: $[-\infty, -2]$. In this case, $C_0, C_1, C_2, C_3$ are the drought categories: mild, moderate, severe, and extreme drought ($z = 3$) and $c_0 =0, c_1 = -1, c_2 = -1.5, c_3 = -2$ are the cutoff value for each class.

Discretise the continuous index into a few labelled categories. For communicating the severity of natural hazard to general public.

uniform workflow to work with index construction.

-   illustration
-   math notation
-   benefit of the pipeline approach
    -   index diagnostic
    -   uncertainty

>>>>

**Spatial aggregation** [TODO]

@@

**Variable transformation ** [TODO]

Variable transformation, and scaling in the next section, are both pre-processing steps that prepare the data with desire statistical property to work with. Some desirable property to work with can be a stable variance, a normal distribution that satisfies modelling assumptions, or a data range that required by the algorithms.
Variable tranformation is a general notion of a functional transformation on the variable: $$h_{\tau}(x(\mathbf{s};\mathbf{t})),$$ where $\tau \in T \subseteq \mathbb{R}^{d_{\tau}}$ is the parameter in the transformation, if any, and $d_{\tau}$ is the number of parameter of $\tau$. Typical examples of variable transformation are log, quadratic, square root, and box-cox transformation.

**Scaling** [TODO]

While scaling can be seen as a specific type of variable tranformation, it is separated into own step to make it explicit in the pipeline.
The key difference between the two steps is that variable transformation typically changes the shape of the data, while scaling only changes the data scale and can usually be written in the form of $$[x(s_i;t_j) - \alpha]/\gamma.$$
For example, a z-score standardisation can be written in the above form with $\alpha = \bar{x}(s; t)$ and $\gamma = \sigma(s; t)$, a min-max standardisation uses $\alpha = \min[x(s_i, t_j)]$ and $\gamma = \max[x(s_i, t_j)] - \min[x(s_i, t_j)]$.
@fig-scale-var-trans-compare shows a collection of variable pre-processing operations and uses color to differentiate whether the operation is a variable transformation or a scaling step. All the scaling operations in green results in the same shape as the original data.

@@

**Dimension reduction** [TODO]

@@

**Benchmarking** [TODO]

@@

In public communication, the index values are usually accompanied by a categorical grade. The categorised grades is an ordered set of descriptive words or colors to communicate the severity or guide the comprehension of the indexes. 
The mapping from continuous index values to the discrete grades is called simplification in the pipeline and it can be written as a piece-wise function:

@@

where $C_0, C_1,\cdots ,C_z$ are the categories and $c_0, c_1, \cdots, c_z$ are the thresholds for each category. In SPI, drought are sorted into four categories: mild drought: $[-0.99, 0]$; moderate drought: $[-1.49, -1]$; severe drought: $[-1.99, -1.5]$, and extreme drought: $[-\infty, -2]$. In this case, $C_0, C_1, C_2, C_3$ are the drought categories: mild, moderate, severe, and extreme drought ($z = 3$) and $c_0 =0, c_1 = -1, c_2 = -1.5, c_3 = -2$ are the cutoff value for each class.

### 2022-11-28 paper/paper.tex
small tweak on simplification and mark TODOs

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, frame hidden, interior hidden, sharp corners, boxrule=0pt, enhanced, breakable]}{\end{tcolorbox}}\fi

@@

\textbf{Spatial aggregation}

@@

\textbf{Variable transformation }

Variable transformation and scaling, in the next section, are both
variable pre-processing steps to prepare the data with desire
statistical property to work with. This can be a more stablised
variance, a normal distribution that satisfies modelling assumptions, or
a data range that required by the algorithms. Variable tranformation is
a general notion of a functional transformation on the variable:
\[h_{\tau}(x(\mathbf{s};\mathbf{t})),\] where
\(\tau \in T \subseteq \mathbb{R}^{d_{\tau}}\) is the parameter in the
transformation, if any, and \(d_{\tau}\) is the number of parameter of
\(\tau\). Typical examples of variable transformation are log,
quadratic, square root, and box-cox transformation.

\textbf{Scaling}

While scaling can be seen as a specific type of variable tranformation,
it is separated into own step to make the scaling operation explicit in
the pipeline. The key difference between the two steps is that variable
transformation typically changes the shape of the data while scaling
only changes the data scale and can usually be written in the form of
\[[x(s_i;t_j) - \alpha]/\gamma.\] For example, a z-score standardisation
can be written in the above form with \(\alpha = \bar{x}(s; t)\) and
\(\gamma = \sigma(s; t)\), a min-max standardisation uses
\(\alpha = \min[x(s_i, t_j)]\) and
\(\gamma = \max[x(s_i, t_j)] - \min[x(s_i, t_j)]\).
Figure~\ref{fig-scale-var-trans-compare} shows a collection of variable
pre-processing operations and uses color to differentiate whether the
operation is a variable transformation or a scaling step. All the
scaling operations in green results in the same shape as the original
data.

@@

\textbf{Dimension reduction}

@@

\textbf{Benchmarking}

@@

where \(C_0, C_1,\cdots ,C_z\) are the categories and
\(c_0, c_1, \cdots, c_z\) are the threshold value in each category. In
SPI, drought are sorted into four categories: mild drought:
\([-0.99, 0]\); moderate drought: \([-1.49, -1]\); severe drought:
\([-1.99, -1.5]\), and extreme drought: \([-\infty, -2]\). In this case,
\(C_0, C_1, C_2, C_3\) are the drought categories: mild, moderate,
severe, and extreme drought (\(z = 3\)) and
\(c_0 =0, c_1 = -1, c_2 = -1.5, c_3 = -2\) are the cutoff value for each
class.

Discretise the continuous index into a few labelled categories. For
communicating the severity of natural hazard to general public.

uniform workflow to work with index construction.

\begin{itemize}
\tightlist
\item
  illustration
\item
  math notation
\item
  benefit of the pipeline approach

  \begin{itemize}
  \tightlist
  \item
    index diagnostic
  \item
    uncertainty
  \end{itemize}
\end{itemize}

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, enhanced, frame hidden, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, breakable, interior hidden]}{\end{tcolorbox}}\fi

@@

\textbf{Spatial aggregation} {[}TODO{]}

@@

\textbf{Variable transformation } {[}TODO{]}

Variable transformation, and scaling in the next section, are both
pre-processing steps that prepare the data with desire statistical
property to work with. Some desirable property to work with can be a
stable variance, a normal distribution that satisfies modelling
assumptions, or a data range that required by the algorithms. Variable
tranformation is a general notion of a functional transformation on the
variable: \[h_{\tau}(x(\mathbf{s};\mathbf{t})),\] where
\(\tau \in T \subseteq \mathbb{R}^{d_{\tau}}\) is the parameter in the
transformation, if any, and \(d_{\tau}\) is the number of parameter of
\(\tau\). Typical examples of variable transformation are log,
quadratic, square root, and box-cox transformation.

\textbf{Scaling} {[}TODO{]}

While scaling can be seen as a specific type of variable tranformation,
it is separated into own step to make it explicit in the pipeline. The
key difference between the two steps is that variable transformation
typically changes the shape of the data, while scaling only changes the
data scale and can usually be written in the form of
\[[x(s_i;t_j) - \alpha]/\gamma.\] For example, a z-score standardisation
can be written in the above form with \(\alpha = \bar{x}(s; t)\) and
\(\gamma = \sigma(s; t)\), a min-max standardisation uses
\(\alpha = \min[x(s_i, t_j)]\) and
\(\gamma = \max[x(s_i, t_j)] - \min[x(s_i, t_j)]\).
Figure~\ref{fig-scale-var-trans-compare} shows a collection of variable
pre-processing operations and uses color to differentiate whether the
operation is a variable transformation or a scaling step. All the
scaling operations in green results in the same shape as the original
data.

@@

\textbf{Dimension reduction} {[}TODO{]}

@@

\textbf{Benchmarking} {[}TODO{]}

@@

where \(C_0, C_1,\cdots ,C_z\) are the categories and
\(c_0, c_1, \cdots, c_z\) are the thresholds for each category. In SPI,
drought are sorted into four categories: mild drought: \([-0.99, 0]\);
moderate drought: \([-1.49, -1]\); severe drought: \([-1.99, -1.5]\),
and extreme drought: \([-\infty, -2]\). In this case,
\(C_0, C_1, C_2, C_3\) are the drought categories: mild, moderate,
severe, and extreme drought (\(z = 3\)) and
\(c_0 =0, c_1 = -1, c_2 = -1.5, c_3 = -2\) are the cutoff value for each
class.
